Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-10-10 Article.tex
Add new figure

%----------------------------------------------------------------------------------
\subsubsection{Experimental validation \label{subsec:ExpValid}}
%----------------------------------------------------------------------------------

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.98\columnwidth]{Figures/drxExpNum}
\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.1~\ps$}.
\label{fig:expNumDRX}
\end{figure}

>>>>

%----------------------------------------------------------------------------------
\subsubsection{\textcolor{purple}{Comparison with some experiments}\label{subsec:ExpValid}}
%----------------------------------------------------------------------------------

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.98\columnwidth]{Figures/drxExpNum}
\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.1~\ps$.}
\label{fig:expNumDRX}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.90\columnwidth]{Figures/ExpNum}
\caption{Experimental and numerical $X_{drx}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}
\label{fig:expNumDRX2}
\end{figure}
